Raft Distributed Consensus Algorithm over WebRTC (Web Real-Time Communication)

### 2015-09-16 research_class/paper.tex
Add a missing article.

To establish a direct communication channel between browsers, WebRTC
uses mechanism called Interactive Connectivity Establishment (ICE)
that is similar to the Session Initiation Protocol (SIP) commonly used
for Voice-over-IP (VoIP) communication \cite{RFC5245:ice}. This
involves a third party server known as a signaling server. Each user
agent (browser) connects to this server at a well known address in
order to establish a direct connection to other user agents. The
signaling server is also uses to communicate session control messages
(open, close, error) and to negotiate media capabilities. %TODO/CITE
The signaling server may optionally provide other services such as
higher level session management, HTTP serving of the web application,
address book service, client presence/availability, etc. %TODO/CITE

>>>>

To establish a direct communication channel between browsers, WebRTC
uses a mechanism called Interactive Connectivity Establishment (ICE)
that is similar to the Session Initiation Protocol (SIP) commonly used
for Voice-over-IP (VoIP) communication \cite{RFC5245:ice}. This
involves a third party server known as a signaling server. Each user
agent (browser) connects to this server at a well known address in
order to establish a direct connection to other user agents. The
signaling server is also uses to communicate session control messages
(open, close, error) and to negotiate media capabilities. %TODO/CITE
The signaling server may optionally provide other services such as
higher level session management, HTTP serving of the web application,
address book service, client presence/availability, etc. %TODO/CITE
